# README

The main file, `margins.R`, shows how to compute Stata-like margins in
R by hand in the context of logistic regression. It's mostly just to
show the intuition underlying Stata's `-margins-` command, but you
can use the results to make nice margins figures with ggplot. Output
from R can be checked in Stata with `margins_check.do` and
`fake_data.csv` can be recreated with `make_fake_data.R`.

For a more complete suite of ready-to-go commands, there's the
[`margins`](https://cran.r-project.org/web/packages/margins/vignettes/Introduction.html)
R package.

## Steps

### Run logistic regression

```{r}
## read in fake data
df <- read.csv('./fake_data.csv')

## run logit
mod <- glm(y ~ x1 + x2 + x3 + x4, data = df, family = binomial(link = 'logit'))
summary(mod)
```

### Margins for unit change in binary variable (x3)

```{r}
## (1) get model matrix from glm() object
mm <- model.matrix(mod)
head(mm)

## (2) drop intercept column of ones b/c we don't need it
mm <- mm[,-1]
head(mm)

## (3) convert to data.frame to make life easier
df_mm <- as.data.frame(mm)
```

### VERSION 1: all other variables `-atmeans-`
**NB: this should be equivalent to Stata `margins x3, atmeans`**

```{r}
## (4) make "new data" where # rows == # margins for key var, averages elsewhere
new_df <- data.frame(x1 = mean(df_mm$x1),
                     x2 = mean(df_mm$x2),
                     x3 = c(0,1),       # two margins, 0/1, for x3
                     x4 = mean(df_mm$x4))

new_df

## (5) use predict() with new data, setting type to get probs
pp <- predict(mod, newdata = new_df, se.fit = TRUE, type = 'response')
pp

## check difference (Stata: -margins, dydx(x3) atmeans-)
pp$fit[2] - pp$fit[1]
```

### VERSION 2: x4 == 1, others `-atmeans-`
**NB: this should be equivalent to Stata `margins x3, at(x4 = 1) atmeans`**

```{r}
## (4) make "new data" where # rows == # margins for key var, averages elsewhere
new_df <- data.frame(x1 = mean(df_mm$x1),
                     x2 = mean(df_mm$x2),
                     x3 = c(0,1),       # two margins, 0/1, for x3
                     x4 = 1)            # x4 == 1

new_df

## (5) use predict() with new data, setting type to get probs
pp <- predict(mod, newdata = new_df, se.fit = TRUE, type = 'response')
pp
```

### Margins for unit change in continuous variable (x1)
**NB: this should be equivalent to Stata `margins, at(x1 = (-4(1)4)) atmeans`**

```{r}
## get idea of range
summary(df$x1)

## (4) make "new data" where # rows == # margins for key var, averages elsewhere
new_df <- data.frame(x1 = seq(from = -4, to = 4, by = 1),
                     x2 = mean(df_mm$x2),
                     x3 = mean(df_mm$x3),
                     x4 = mean(df_mm$x4))

new_df

## (5) use predict() with new data, setting type to get probs
pp <- predict(mod, newdata = new_df, se.fit = TRUE, type = 'response')
format(pp, scientific = FALSE)
```